Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation

### 2020-09-22 Article/ici_submm_cloudcorr.tex
added missing Figures

Fig.~\ref{fig:posterior_distribution_I2V} presents examples of the predicted quantiles for three different corrected observations of the ICI I1V channel. The three cases have a similar median value but very different spread of the remaining quantiles. These examples illustrate the case of very similar corrected observation values (the estimated median) but with different estimated observation errors.
For an analysis of QRNN predictions, a point estimate of the posterior distribution is required. Usually for Bayesian analysis, the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value. The distribution of point estimates is shown in Fig.~\ref{fig:PDF_predictions}. For all three channels, an excellent agreement between the predictions and simulations is observed. This indicates that QRNN is successful in predicting NFCS values for majority of the cases. At lower brightness temperatures, the frequency of predictions is slightly smaller than simulations. This could be due to few QRNN predictions ending up with partially corrected cloud impact.

@@

Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors. The predicted dataset is constructed by drawing random samples from the posteriori distribution. We do derive any sample from outside $\pm3\sigma$. The predicted error is deviation of random sample to its median. For QRNN-single, the predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically. For QRNN-all, the predicted and observed errors have a better agreement and the spread is symmetric for the former. The results show that both QRNN-single and QRNN-all are not able to represent the left wings of the distribution. This could also be a sampling issue, as the high errors we try to predict form a very small fraction of the complete dataset.

@@

The five channels are sensitive to different regions of the troposphere so not all clouds get equal representation in each. The cloud impact from regions where the weighting functions match poorly cannot be represented adequately in QRNN. However,the brightness temperature of same cloud measured at different frequencies can be valuable to train QRNN.  Similarly, the clear-sky measurements from different channels can effectively cancel out the noise. QRNN predictions can be interpreted as a weighted average between the multiple channels. As clear-sky cases occur more frequently, the averaging can cancel out noise.

Finally, we investigate if uncertainty estimates from QRNN-mwi are representative of prediction errors. Fig.~\ref{fig:uncertainty_cloud_impact} displays the average prediction uncertainty in 97\% confidence interval for different cloud impacts. For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness. As fraction of cloud impact increases, the predictions become increasingly uncertain. Most uncertain predictions occur for the outermost channels (MWI-14, MWI-15). These channels also have the lowest prediction accuracy.

@@

These results show that even though ICI and MWI are two different instruments, their channels can benefit from each other. Although re-mapping to a common footprint would slighly compromise the data quality, a high accuracy achieved with simulations suggests that the QRNN would work well even when actual measurements are available.

@@

In an analogy between the results from ICI channels, we perform a similar error distribution analysis 
and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}. For channel AWS-32, the average bias and standard deviation in the prediction errors is is -1.34\,K and 5.91\,K respectively. However, after correction, the bias and standard deviation are -0.08\,K and 1.0\,K. A decrease in the skewness of error distributions is evident(from -7.48 to -1.52), but a relatively high values after prediction indicate presence of cases with partially-corrected cloud impact. For AWS-33, the predictions have slightly higher accuracy than AWS-32. The MAE in predictions is only 0.50\,K in comparison to 1.23\,K for the measurements. Similar results are also seen for AWS-35 and AWS-36. For both channels, the predictions are relatively more symmetric than the other channels. Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of predictions is narrower than noise.

Overall the results demonstrate that QRNN is successful in predicting the NFCS data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32. The prediction error distributions are symmetric with low bias and standard deviation. The cases with high error are mostly associated with high cloud impact and constitute only a small fraction of the total dataset. Excluding such cases decreases the variability in the predictions and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise. Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two channels. Since the noise in the two channels are stationary and uncorrelated, the predictions benefit from the additional information, but the noise component tends to cancel out. For AWS-32, QRNN is only partially successful in reducing the impact of hydrometeors. The prediction errors have significantly lower spread than the measurements, but cases with partially corrected cloud impact deteriorates the overall accuracy. Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, the testing data will inevitably contain cases for which QRNN has not trained for. Prediction for such cases would be inaccurate and highly uncertain. In such cases, the predictions should be used with caution.

>>>>

Fig.~\ref{fig:posterior_distribution_I1V} presents examples of the predicted quantiles for three different corrected observations of the ICI I1V channel. The three cases have a similar median value but very different spread of the remaining quantiles. These examples illustrate the case of very similar corrected observation values (the estimated median) but with different estimated observation errors.
For an analysis of QRNN predictions, a point estimate of the posterior distribution is required. Usually for Bayesian analysis, the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value. The distribution of point estimates is shown in Fig.~\ref{fig:PDF_predictions}. For all three channels, an excellent agreement between the predictions and simulations is observed. This indicates that QRNN is successful in predicting NFCS values for majority of the cases. At lower brightness temperatures, the frequency of predictions is slightly smaller than simulations. This could be due to few QRNN predictions ending up with partially corrected cloud impact.

@@

Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors. The predicted dataset is constructed by drawing random samples from the posteriori distribution. We do not derive any sample from outside $\pm3\sigma$.  The predicted error is deviation of random sample to its median. For QRNN-single, the predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically. For QRNN-all, the predicted and observed errors have a better agreement and the spread is symmetric for the former. The results show that both QRNN-single and QRNN-all are not able to represent the left wings of the distribution. This could also be a sampling issue, as the high errors we try to predict form a very small fraction of the complete dataset.

@@

The five frequencies are sensitive to different regions of the troposphere so not all clouds are equally represented in all. The brightness temperature of same cloud measured at different frequencies can be valuable to train QRNN. However the hydrometeor impact from regions where the weighting functions match poorly cannot be represented adequately in QRNN. As a consequence, the predictions are poor. In constrast, the clear-sky measurements of the same scene from multiple channels, reinforces the QRNN predictions. The measurement noise in all channels is stationary and uncorrelated, thus the predictions benefit from the additional information, and averaging cancels out the noise component. As clear-sky cases occur more frequently, the effect is quite prominent.

Further, we investigate if uncertainty estimates from QRNN-mwi are representative of prediction errors. Fig.~\ref{fig:uncertainty_cloud_impact} displays the average predicted errors in 94\% confidence interval, for different cloud impacts. For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness. As fraction of cloud impact increases, the predictions become increasingly uncertain. Most uncertain predictions occur for the outermost channels (MWI-14, MWI-15). These channels also have the lowest prediction accuracy.  Thus, the QRNN predictions possess a multivariate representation of uncertainty. The uncertainty of cases with varying cloud impacts can be expressed individually.

@@

These results show that even though ICI and MWI are two different instruments, their channels can benefit from each other. Although re-mapping to a common footprint would slighly compromise the data quality, a high accuracy achieved with simulations suggests that the QRNN would work well when actual measurements are available.

@@

In an analogy between the results from ICI channels, we perform a similar error distribution analysis 
and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}. For channel AWS-32, the average bias and standard deviation in the prediction errors is -1.34\,K and 5.91\,K respectively. However, after correction, the bias and standard deviation are -0.08\,K and 1.0\,K. A decrease in the skewness of error distributions is evident, but a relatively high values after prediction indicate presence of cases with partially-corrected cloud impact. For AWS-33, the predictions have slightly higher accuracy than AWS-32. The MAE in predictions is only 0.50\,K in comparison to 1.23\,K for the measurements. Similar results are also seen for AWS-35 and AWS-36. For both channels, the error distributions are relatively more symmetric than the other channels. Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise.

Overall the results demonstrate that QRNN is successful in predicting the NFCS data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32. The prediction error distributions are symmetric with low bias and standard deviation. The cases with high error are mostly associated with high cloud impact and constitute only a small fraction of the total dataset. Excluding such cases decreases the errors and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise. Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two channels. For AWS-32, QRNN is only partially successful in reducing the impact of hydrometeors. The prediction errors have significantly lower spread than the measurements, but cases with partially corrected cloud impact deteriorates the overall accuracy. Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, the testing data will inevitably contain cases for which QRNN has not trained for. Prediction for such cases would be inaccurate and highly uncertain. In such cases, the predictions should be used with caution.
